---
title: "Project EDA"
author: "Yash Manne"
date: "02/04/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tinytex)
library(knitr)
library(latex2exp)
library(tidyverse)
```

## Data Source

[Data](https://www.kaggle.com/datasets/danielgrijalvas/movies?resource=download) scraped from IMDb but hosted on Kaggle.

#### Features:
* `budget`: the budget of a movie. Some movies don't have this, so it appears as 0
* `company`: the production company
* `country`: country of origin
* `director`: the director
* `genre`: main genre of the movie.
* `gross`: revenue of the movie
* `name`: name of the movie
* `rating`: rating of the movie (R, PG, etc.)
* `released`: release date (YYYY-MM-DD)
* `runtime`: duration of the movie
* `score`: IMDb user rating
* `votes`: number of user votes
* `star`: main actor/actress
* `writer`: writer of the movie
* `year`: year of release

Consists of 7668 movies from 1980-2020.

```{r}
df = read.csv('movies.csv')
```

```{r}
p1 = df %>% ggplot(mapping = aes(x= gross, y=score)) +
  geom_point(alpha=0.25) + theme_bw()
p2 = df %>% ggplot(mapping = aes(x= budget, y=score)) +
  geom_point(alpha=0.25) + theme_bw()
p3 = df %>% ggplot(mapping = aes(x= budget, y=gross)) +
  geom_point(alpha=0.25) + theme_bw()
p4 = df %>% ggplot(mapping = aes(x= year, y=runtime)) +
  geom_point(alpha=0.25) + theme_bw()

cowplot::plot_grid(p1,p2,p3,p4,
  ncol = 2, nrow = 2
)
```


```{r}
simpleLinReg <- lm(gross~ budget, data = df)
summary(simpleLinReg)
std_errors = sqrt(diag(vcov(simpleLinReg)))
# percError <- summary(simpleLinReg)$sigma / mean(pros$lcavol) * 100
```

The estimate of the y-intercept coefficient is `r simpleLinReg$coefficients[1]`, with a standard error of `r std_errors[1]`.
The estimate of the slope coefficient is `r simpleLinReg$coefficients[2]`, with a standard error of `r std_errors[2]`.


### Statistical test of the null hypothesis of no linear association between movie budget and gross revenue.

The **null hypothesis** is that there is no linear association between the predictor variable, `budget`, and the response variable, `gross`, or that the true slope coefficient is 0.
  
  $$H_0: \beta_1 = \beta_{1,0}  \text{ or } \beta_1  = 0$$
  
The **alternative hypothesis** is that there is a linear association between the predictor variable, `budget`, and the response variable, `gross`, or that the true slope coefficient is not 0.

  $$H_A: \beta_1 \neq \beta_{1,0} \text{ or } \beta_1  \neq 0$$
  
Then, we define our test statistic, $T$ as $T = \frac{\hat{\beta_1 - \beta_{1,0}}}{\widehat{SE}(\hat{\beta_1})} = \frac{\hat{\beta_1}}{\widehat{SE}(\hat{\beta_1})}$, where $T \sim t_{n-2}$. In other words $T$ follows a t-distribution with $n-2$ degrees of freedom, where $n$ is the total number of observations. In this case, $n=5436$, so the test statistic has 5434 degrees of freedom. 

```{r}
b1_statistic = coef(
  summary(simpleLinReg)
)[2,]
b1_statistic[4]
```

Based on the summary, we can see that the t-statistic for $\beta_1$ is `r b1_statistic[3]` with a p-value of `r b1_statistic[4]`. Since the p-value is less than the significance value of 0.05, we can reject the null hypothesis.

